\documentclass[10pt,a4paper]{report}
\usepackage[top=1in, left=0.5in, right=0.5in, bottom=1.5in]{geometry}
\usepackage{titlesec}
\usepackage{tabulary}
\usepackage{tabularx}

\pagenumbering{gobble}
\begin{document}
% Title
\begin{center}
	{\Large Design and Analysis: {\bfseries Rust Evaluation}}
	- {\large{\itshape Ethan Larkham} and {\itshape Todd Gaunt}}
	- {\large October 13, 2017}
\end{center}
\vspace{0.5em}
\paragraph{Overview Of Problem}
This project aims to compare differences between languages fairly
and display the results in a format that is easily understood while avoiding
any statistical pitfalls.
\paragraph{Reason For The Project}
Since rust is a new programming language that touts its "fearless" concurrency,
we will be comparing and analyzing how rust handles concurrency in contrast
with its more dominant competitor C++, using pthreads as its concurrency method.
The hope is that by the end of this project, the advantages of rust's
model over competitors will be brought to light.
\paragraph{High Level Design}
The end product of this project will be a research paper, a poster, and a
project repository containing all of the code used to gather the for the report
that anyone can access to reproduce the results. The report contain a detailed
write-up on the differences found between performance benchmarks, differences
between generated assembler, and the subjective report on language ergonomics.
As an aid to the report, the poster will have the most interesting performance
graphs displayed in larger detail, but will omit most of the subjective
language details and won't contain any assembler analysis (due to it not being
graphic in nature).
\paragraph{Design Details}
\begin{flushleft}
	\begin{itemize}
		\item The project will consist of many small functionally
			identical programs implemented in both rust and C++.
		\item Analysis of the two languages will primarily be done using clang++
			and rustc since both produce llvm, g++ will be used secondarily and
			treated as a control.
		\item C++ implementations will use pthreads instead of the native C++
			threads.
		\item C++/Rust Jacobi Implementation.
	\end{itemize}
\end{flushleft}
\paragraph{Current Backlog}
\begin{flushleft}
	\begin{itemize}
		\item C++/Rust Jacobi Analysis.
		\item C++/Rust Concurrent Hash Table Implementation and Analysis.
	\end{itemize}
\end{flushleft}
\paragraph{Sprint Analysis}
Overall the goals of each sprint were met with a little bit of lag time that
spilled over to the final presentation week. Each sprint so far has involved at least one major accomplishment, but usually
two (one from each member). A reasonable amount of the project
has been completed (2 out of the 5 programs, along with some analysis), and to
make up for the lost time work on the project will continue over Winter break.
\paragraph{Review Of Team Performance}
The team slightly underestimated the time needed for setting up the analysis
tools and as a result the presentation lacked visual data about the jacobi
program implementations. Overall though, most of what was intended to be accomplished
this semester was accomplished.
\paragraph{Changes For Second Semester}
Fewer milestones are scheduled for the second semester than the first, and some have
been moved into the Winter break.
\end{document}
