\documentclass[10pt,a4paper]{report}
\usepackage[top=1in, left=0.5in, right=0.5in, bottom=1.5in]{geometry}
\usepackage{titlesec}
\usepackage{tabulary}
\usepackage{tabularx}

\pagenumbering{gobble}
\begin{document}
% Title
\begin{center}
	{\Large The Writing Plan: {\bfseries Rust Evaluation}}
	- {\large{\itshape Ethan Larkham} and {\itshape Todd Gaunt}}
	- {\large October 13, 2017}
\end{center}
\vspace{0.5em}
\paragraph{Description of the final project}
The charter will include the detailed overview of the project, project sponsor
information, MOV details, what is both in and out of scope, a high level
schedule with milestones, resources assigned to projects, assumptions and
risks, dependencies, constraints (if any), and project administration details.
\paragraph{Outline of the content covered by project}
\begin{flushleft}
	\begin{itemize}
		\item Performance Analysis
		\item Assembly Analysis
		\item Analysis of language ergonomics
		\item Analysis of language features
		\item Comparison between both languages
	\end{itemize}
\end{flushleft}
\paragraph{Responsibility}
Each program will have three main sections in the report: One for the C++
implementation, another for the Rust implementation, and finally a comparison
between the two. It will be the responsibility of whoever implemented the
program will be responsible for the language-specific analysis for the
respective language used. The comparison section will be done as a
collaboration between team members.
\paragraph{Tentative Schedule}
The report will be completed in sections after each program is implemented.
\paragraph{Information Gathering Strategy}
The analysis will mostly consists of data generated by the project, otherwise
language documentation will be consulted for information. All findings that
might be useful to all members will be posted on Trello for easy access.
\paragraph{Review and Editing Process}
The report will be written as a LaTeX document and will be updated and reviewed
using git to make incremental changes and comments.
\paragraph{Final Product}
Todd will be responsible for the final edit, and it will be finished when it
gets approval from both team members.
\end{document}
